The eclipse of the V773 Tau B circumbinary disk

### 2022-06-18 src/tex/ms.tex
added C orbit plots
ms typo and redid figs

\newcommand\todo[1]{\colorbox{yellow}{\textcolor{red}{#1}}}
\newcommand{\RGM}[1]{\textcolor{cyan}{#1}}

@@

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_b_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau AB system.
        %
        A is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
\label{fig:v773orbitize}
\end{center}
\end{figure*}

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_c_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau C system.
        %
        The barycentre of AB is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
\label{fig:v773Corbitize}
\end{center}
\end{figure*}

@@

There is, however, the matter of orbital stability within a hierarchical triple, and we can approximate the V773 Tau system with A and B forming an inner binary and C the distant third component orbiting them.
%
Using the approximations within \citet{Eggleton95}, we can calculate a lower limit for the periastron of C around the AB system, and then reject orbits from the orbital bundle produced from our fitting procedure. \RGM{This stability criteria is able to predict the stability over timescales of $5\times 10^5\,P_{AB}$ \citep{He2018}, much longer than the age of the system.}
% 
With $q_{in}=M_A/M_B=1.24$ and $q_{out}\geq 7.5$ and $a_{AB}=15.3au$ and $e_{AB} = 0.1$ this yields $Y^{min}_0=4.06$ and using Equation 2 from \citet{Eggleton95} we can derive a lower limit for the periastron distance of C.
%
Trial masses for C vary from 0.4 to 0.7 $M_\odot$ and only weakly change the periastron distance for C, so we set it at 68 au.
%
After removing orbits with periastron distances smaller than this, we use this new bundle of orbits as the starting point for a second optimization run.
%
The resultant orbital bundles show convergence and the triangle plot of the eccentricity and inclination of the orbit of C are very well constrained, as shown in Figure~\ref{fig:v773caei}, most notably that the inclination of C is $97\pm1$\degr{} with a tightly constrained eccentricity of 0.40.
%
The asymmetry of the errors on the orbital elements reflect the wide range of possible orbits as shown in Table~\ref{tab:orbs}.

\begin{figure}[ht]
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/v773_c_a_e_i_corner_plot.pdf}
        \caption{Correlation between the semi-major axis, eccentricity and orbital inclination of the V773 Tau C system.
        }
\label{fig:v773caei}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/particle.eps}
    \caption{Particle nodal precession timescale and the KL timescale as a function of the particle separation from  the BaBb binary. 
    %
    The blue ($e_{\rm b}=0.2$),  orange ($e_{\rm b}=0.5$) and green ($e_{\rm b}=0.8$) lines show the nodal precession timescales.
    %
    The red line shows the KL timescale.
    %
    The particle is unstable if  the nodal precession timescale is longer than the KL timescale \citep{Verrier2009}. }
\label{fig:particles}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/compare.eps}
    \caption{The disk nodal precession timescale (blue) and the KL timescale (orange) as a function of the eccentricity of the BaBb binary.
    %
    The disk can remain polar if the nodal precession timescale is shorter than the KL timescale.  }
\label{fig:timescales}
\end{center}
\end{figure}

>>>>

\newcommand\todo[1]{\colorbox{yellow}{\textcolor{red}{#1}}}

@@

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_b_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau AB system.
        %
        A is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
      \label{fig:v773orbitize}
 %     \script{analyze_and_plot_C_orbit_bundle.py}
\end{center}
\end{figure*}

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_c_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau C system.
        %
        The barycentre of AB is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
    \label{fig:v773Corbitize}
    \script{analyze_and_plot_C_orbit_bundle.py}
\end{center}
\end{figure*}

@@

There is, however, the matter of orbital stability within a hierarchical triple, and we can approximate the V773 Tau system with A and B forming an inner binary and C the distant third component orbiting them.
%
Using the approximations within \citet{Eggleton95}, we can calculate a lower limit for the periastron of C around the AB system, and then reject orbits from the orbital bundle produced from our fitting procedure. This stability criteria is able to predict the stability over timescales of $5\times 10^5\,P_{AB}$ \citep{He2018}, much longer than the age of the system.
% 
With $q_{in}=M_A/M_B=1.24$ and $q_{out}\geq 7.5$ and $a_{AB}=15.3au$ and $e_{AB} = 0.1$ this yields $Y^{min}_0=4.06$ and using Equation 2 from \citet{Eggleton95} we can derive a lower limit for the periastron distance of C.
%
Trial masses for C vary from 0.4 to 0.7 $M_\odot$ and only weakly change the periastron distance for C, so we set it at 68 au.
%
After removing orbits with periastron distances smaller than this, we use this new bundle of orbits as the starting point for a second optimization run.
%
The resultant orbital bundles show convergence and the triangle plot of the eccentricity and inclination of the orbit of C are very well constrained, as shown in Figure~\ref{fig:v773caei}, most notably that the inclination of C is $97\pm1$\degr{} with a tightly constrained eccentricity of 0.40.
%
The asymmetry of the errors on the orbital elements reflect the wide range of possible orbits as shown in Table~\ref{tab:orbs}.

\begin{figure}[ht]
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/v773_c_a_e_i_corner_plot.pdf}
        \caption{Correlation between the semi-major axis, eccentricity and orbital inclination of the V773 Tau C system.
        }
    \label{fig:v773caei}
    \script{analyze_and_plot_C_orbit_bundle.py}

\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/particle.pdf}
    \caption{Particle nodal precession timescale and the KL timescale as a function of the particle separation from  the BaBb binary. 
    %
    The blue ($e_{\rm b}=0.2$),  orange ($e_{\rm b}=0.5$) and green ($e_{\rm b}=0.8$) lines show the nodal precession timescales.
    %
    The red line shows the KL timescale.
    %
    The particle is unstable if  the nodal precession timescale is longer than the KL timescale \citep{Verrier2009}. }
\label{fig:particles}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/compare.pdf}
    \caption{The disk nodal precession timescale (blue) and the KL timescale (orange) as a function of the eccentricity of the BaBb binary.
    %
    The disk can remain polar if the nodal precession timescale is shorter than the KL timescale.  }
\label{fig:timescales}
\end{center}
\end{figure}
